Holomorphic field theories and higher algebra

### 2024-10-08 draft.tex
these must be minor

@@

In general, Eager's suggestion opens up a fascinating vein of inquiry:
\begin{quote}
how do physical results about supersymmetric gauge theories behave under twisting to holomorphic or topological theories?
\end{quote}
We have found, so far, that these results often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
provided their quantizations, and began analyzing their factorization algebras.
One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}. 
A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.

>>>>

\og{Discuss twist along circle by automorphism of algebra. Forward ref to example later.}

@@

In general, Eager's suggestion opens up a fascinating vein of inquiry:
\begin{quote}
how do physical results about supersymmetric gauge theories behave under twisting to holomorphic or topological theories?
\end{quote}
We have found, so far, that these results often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
provided their quantizations, and began analyzing their factorization algebras.
One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
The answer to this question has been studied by Raghavendran and Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}. 
A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.
